Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-15 longoutput.tex
Clean up and fix bugs
Do work that was required due to creating theorems

Here we construct a transform that we will use to... TODO Editorial intro.

\begin{theorem}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of $T$ gates, each either $H$ or $\Lambda(P(i))$.
		\item uses $n$ qubit, including ancillaries.
	\end{itemize}
	Then a classical machine, given $C$ and some classical $x$, can compute a circuit $C'$ and a classical string $x'$ that:
	\begin{itemize}
		\item $C'$ consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
		\item $C'$ uses $n+1$ qubits.
		\item All states are real (including initial, intermediate states, and output).
		\item The measurement results of $C(x)$ and the first $n$ qubits of $C'(x')$ are identically distributed.
	\end{itemize}
\end{theorem}

\begin{proof}

Now consider a circuit $C=U_T\ldots U_1$ with the following properties:
\begin{itemize}
	\item $U_i\in\set{H, \Lambda(P(i))}$
	\item Has initial state $\ket\psi$ with $n$ qubits
\end{itemize}

We first reduce it to use only real gates and states. The proof is taken from \cite{quant-ph/0301040}. We consider the transform
$$\mathcal{F}(\ket{\phi})=\ket{0}\otimes\Re\ket{\phi}+\ket{1}\otimes\Im\ket{\phi}$$
where $\Re$ and $\Im$ denote real and imaginary parts respectively. It has the following properties

\begin{itemize}
	\item $\forall\ket\phi$, $\mathcal{F}(\ket\phi)$ is real.
	\item Preserves $X$ and $Z$ measurement results
\end{itemize}

We now apply $\mathcal{F}$ to $\ket\psi$. To make the notation easier, let $\ket{\psi}$ be 1-indexed, and the $\mathcal{F}\ket{\psi}$ be 0-indexed, so corresponding qubits stay in the same position.

The transform commutes with Hadamard gates on the respective qubit, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
\end{proof}

Now we also prove a theorem about the circuit after transformation that we'll use later.

@@

To simplify the notation, we may only write the qubits with $X$ and $Z$ operators when talking about members of $\mathcal{G}_{XZ}$.

\begin{theorem}
	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$
\end{theorem}

@@

Here we reduce a circuit into a local Hamiltonian instance with a few additional properties as below.

\begin{theorem}
	Let $C$ be a circuit such that:
	\begin{itemize}
		\item $C=U_T\ldots U_1$, where $U_i$ are either $H$ or $\Lambda^2(X)$
	\end{itemize}
	Let $x$ be a classical string. Then a classical machine can construct in polynomial time a local Hamiltonian instance such that:
	\begin{itemize}
		\item its ground state is $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$ where $y$ is $x$ possibly concatenated with ancillaries.
		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
		\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
		\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

\begin{proof}

Let $C$ be a circuit with the above properties. Define the following quantities.
\begin{itemize}
	\item Let $y$ denote the initial state. That is, $x$ possibly concatenated with ancillaries.
	\item Let $y_i$ denote the $i$-th bit of $y$
	\item Let $n$ be the number of qubits in $C$
\end{itemize}

We then attempt to construct a local Hamiltonian with the following ground state that encodes the history of the computation: $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.

@@

Now we consider the kernels of the Hamiltonians we defined. Notice the following.
$$K_{clock}=\ker H_{clock}$$
$$K_{in}=\ker H_{in}$$
$$K_{prop}=\ker H_{prop}$$
$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\psi_{circuit}}$$
We now consider the space outside the desired state.
$$S=(\spn\set{\psi_{circuit}})^\bot$$
$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
To combine the Hamiltonians, we apply the projection lemma twice.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(n)=O(T)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
\end{proof}

>>>>

Here we construct a way to preprocess and simplify the circuit to a form that's easy for us to work with.

\begin{theorem}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of $T$ gates, each either $H$ or $\Lambda(P(i))$.
		\item uses $n$ qubit, counting ancillaries.
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
		\item uses $n+1$ qubits, counting ancillaries.
		\item $\forall x\in\set{0,1}^*$, the $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x)$ are identically distributed.
	\end{itemize}
\end{theorem}

\begin{proof}
The proof is taken from \cite{quant-ph/0301040}. We consider the transform
	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
where $\Re$ and $\Im$ denote real and imaginary parts respectively. It is easy to check that this preserves $X$ and $Z$ measurement results.

This transform commutes with Hadamard gates on the respective qubit, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
\end{proof}

Now we also prove a theorem about the transformed circuit that we'll use later.

@@

\begin{theorem}
	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
\end{theorem}

@@

Here we reduce a circuit into a local Hamiltonian instance with a few additional properties.

\begin{theorem}
	Let $C=U_T\ldots U_1$ where $U_i$ are either $H$ or $\Lambda^2(X)$, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time a local Hamiltonian instance such that:
	\begin{itemize}
		\item its ground state is $$\ket{\psi_{circuit}}=\sum_{t=0}^TU_t...U_1\ket{y}\otimes\ket{\hat{t}}$$ where $y$ is $x$ possibly concatenated with ancillaries.
		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
		\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
		\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

\begin{proof}
	We construct the Hamiltonian by ensuring states perpendicular to $\ket{\psi_{circuit}}$ have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.

Let $y_i$ denote the $i$-th bit of $y$, and let $n$ be the number of qubits in $C$.

@@

To properly combine the three Hamiltonians defined, we consider the kernels of the Hamiltonians we defined.
$$K_{clock}=\ker H_{clock}$$
$$K_{in}=\ker H_{in}$$
$$K_{prop}=\ker H_{prop}$$
Notice that
$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{circuit}}}$$
We now consider the space outside the desired state.
$$S=(\spn\set{\ket{\psi_{circuit}}})^\bot$$
$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
To combine the Hamiltonians, we apply the projection lemma twice.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(n)=O(T)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
\end{proof}
